Analyses

### 2024-07-10 analyses.Rmd
- updated manuscript - removed typos - extended theory

```{r results='hide', cache=F}
# install github packages
# devtools::install_github("tdienlin/td@v.0.0.2.3")  # uncomment to install
# devtools::install_github("yrosseel/lavaan")

@@

# load packages
lapply(
  packages, 
  library, 
  character.only = TRUE, 
  quietly = TRUE
  )

@@

```{r}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>%
  print()

# export factor validity
assign(
  paste0(
    name, 
    "_facval"
    ), 
  facval
  )
```

@@

```{r}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>% 
  print()

@@

```{r warning=T}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>% 
  print()

@@

```{r cache=F}
# extract model factor scores / predicted values for items & calc means
d_fs <- 
  lavPredict(
    fit_baseline, 
    type = "ov"
    ) %>% 
  as.data.frame() %>% 
  mutate(
    version = d$version, 
    grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
    grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
    pri_con_fs = rowMeans(select(., starts_with("PC01"))),
    trust_gen_fs = rowMeans(select(., starts_with("TR02"))),
    trust_spec_fs = rowMeans(select(., starts_with("TR01"))),
    pri_del_fs = rowMeans(select(., starts_with("PD01"))),
    self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
  select(
    version, 
    pri_con_fs, 
    grats_gen_fs, 
    grats_spec_fs, 
    pri_del_fs, 
    self_eff_fs, 
    trust_gen_fs, 
    trust_spec_fs, 
    words_log
    )

@@

# means of model predicted values
des <- 
  rbind(
    des_pricon,
    des_gratsgen,
    des_gratsspec,
    des_pridel,
    des_trustgen,
    des_trustspec,
    des_selfeff
    )

facval_tab <- 
  rbind(
    pricon_facval,
    gratsgen_facval,
    gratsspec_facval,
    pridel_facval,
    selfeff_facval,
    trustgen_facval,
    trustspec_facval
    ) %$%
  cbind(
    des[-c(8), ],
    .
    ) %>%
  set_rownames(
    var_names[-c(8)]
    )

facval_tab %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

>>>>

```{r results='hide', cache=F}
# install github packages
# devtools::install_github("tdienlin/td@v0.0.2.6")  # uncomment to install
# devtools::install_github("yrosseel/lavaan")

@@

# load packages
lapply(
  packages
  # , install.packages
  , library
  , character.only = TRUE
  , quietly = TRUE
  )

@@

```{r}
facval <- 
  fit_tab(
    fit, 
    # reliability = TRUE, 
    # scaled = TRUE
    ) %T>%
  print()
```

@@

```{r}
facval <- 
  fit_tab(
    fit, 
    # reliability = TRUE, 
    # scaled = TRUE
    ) %T>% 
  print()

@@

```{r warning=T}
facval <- 
  fit_tab(
    fit, 
    # reliability = TRUE, 
    # scaled = TRUE
    ) %T>% 
  print()

@@

```{r cache=F}
# extract model factor scores / predicted values for items & calc means
d_fs <- 
  lavPredict(
    fit_baseline, 
    type = "ov"
    ) %>% 
  as.data.frame() %>% 
  mutate(
    version = d$version, 
    grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
    # grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
    pri_con_fs = rowMeans(select(., starts_with("PC01"))),
    trust_gen_fs = rowMeans(select(., starts_with("TR02"))),
    trust_spec_fs = rowMeans(select(., starts_with("TR01"))),
    pri_del_fs = rowMeans(select(., starts_with("PD01"))),
    self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
  select(
    version, 
    pri_con_fs, 
    grats_gen_fs, 
    # grats_spec_fs, 
    pri_del_fs, 
    self_eff_fs, 
    trust_gen_fs, 
    trust_spec_fs, 
    words_log
    )

@@

# means of model predicted values
des <- 
  rbind(
    des_pricon,
    des_gratsgen,
    # des_gratsspec,
    des_pridel,
    des_trustgen,
    des_trustspec,
    des_selfeff
    )

facval_tab <- 
  rbind(
    pricon_facval,
    gratsgen_facval,
    # gratsspec_facval,
    pridel_facval,
    selfeff_facval,
    trustgen_facval,
    trustspec_facval
    ) %$%
  cbind(
    des[-c(8), ],
    .
    ) %>%
  set_rownames(
    var_names[-c(7)]
    )

facval_tab %>% 
  kable() %>% 
  kableExtra::kable_styling("striped") %>% 
  kableExtra::scroll_box(width = "100%")
```
